Congress text mining

### 2022-11-29 slides/slides.qmd
Update slides.qmd

-   between 2016 and 2022 there have been major shifts in terms of majorities in the US congress:

@@

-   We will focus on the question on whether and how the different majorities had an impact on the policies that have been passed by Congress.

>>>>

::: columns
::: {.column width="80%"}
-   between 2016 and 2022 there have been major shifts in terms of majorities in the US congress:

@@

-   We will focus on the question on whether and how the different majorities had an impact on the policies that have been passed by Congress.
:::

::: {.column width="20%"}
![](https://www.politico.com/dims4/default/0ba7efa/2147483647/strip/true/crop/1160x773+0+0/resize/1290x860!/quality/90/?url=https%253A%252F%252Fstatic.politico.com%252Fa3%252F2c%252Ffbd235e445b4a96e0373e3060e3c%252Fgettyimages-1294351903-1.jpg){width="300"}
:::
:::
